Galois Characterization of Function Fields of \\ Transcendence Degree $1$ over Number Fields

### 2016-12-14 Master Thesis/synopsis.tex
Comment out 2.3

\begin{lemma}\phantomsection\label{2.3}
\begin{enumerate}[(i)]
\item $\operatorname{Spv}(K)$, together with the maps $\pi_{\mathfrak{X}}$, is the projective limit of topological spaces: 
\[\operatorname{Spv}(K) =\varprojlim_{\mathfrak{X}\in\mathfrak{M}(K)}\mathfrak{X}\]
In particular we have:
\[ |\operatorname{Spv}(K)| =\varprojlim_{\mathfrak{X}\in\mathfrak{M}(K)}|\mathfrak{X}| \]
\item For all $v\in\operatorname{Spv}(K)$ we have:
\[ \mathcal{O}_v = \varinjlim_{\mathfrak{X}\in\mathfrak{M}(K)}\mathcal{O}_{\mathfrak{X},\pi_\mathfrak{X}(v)} \]
\item For $v\in\operatorname{Spv}(K)$ let $K_v$ be the quotient field of a henselization of $\mathcal{O}_v$ and for $\mathfrak{X}\in\mathfrak{M}(K),\ x\in\mathfrak{X}$ let $K_\mathfrak{X}$ be the quotient field of a henselization of $\mathcal{O}_{\mathfrak{X},x}$. Then:
\[ K_v=\varinjlim_{\mathfrak{X}\in\mathfrak{M}(K)}K_{\pi_\mathfrak{X}(v)} \]
\end{enumerate}
\end{lemma}

@@

\begin{definition}
For each admissible $S\subset X_0$ and $T_1\subset X_0\setminus S$ with injective $r_{S,T_1}$ we also have the injectivity of $r_{S,T_2}$ for every $T_2 \supset T_1$. Therefore,  we can find a finite subset $T\subset X_0\setminus S$ such that both $r_{S,T}$ and $r_{S',T'}$ are injective. Such a $T$ will be called $S$-\textit{admissible} and $(S,T)$ is called \textit{admissible pair}.
\end{definition}

>>>>

\iffalse
\begin{lemma}\phantomsection\label{2.3}
\begin{enumerate}[(i)]
\item $\operatorname{Spv}(K)$, together with the maps $\pi_{\mathfrak{X}}$, is the projective limit of topological spaces: 
\[\operatorname{Spv}(K) =\varprojlim_{\mathfrak{X}\in\mathfrak{M}(K)}\mathfrak{X}\]
In particular we have:
\[ |\operatorname{Spv}(K)| =\varprojlim_{\mathfrak{X}\in\mathfrak{M}(K)}|\mathfrak{X}| \]
\item For all $v\in\operatorname{Spv}(K)$ we have:
\[ \mathcal{O}_v = \varinjlim_{\mathfrak{X}\in\mathfrak{M}(K)}\mathcal{O}_{\mathfrak{X},\pi_\mathfrak{X}(v)} \]
\item For $v\in\operatorname{Spv}(K)$ let $K_v$ be the quotient field of a henselization of $\mathcal{O}_v$ and for $\mathfrak{X}\in\mathfrak{M}(K),\ x\in\mathfrak{X}$ let $K_\mathfrak{X}$ be the quotient field of a henselization of $\mathcal{O}_{\mathfrak{X},x}$. Then:
\[ K_v=\varinjlim_{\mathfrak{X}\in\mathfrak{M}(K)}K_{\pi_\mathfrak{X}(v)} \]
\end{enumerate}
\end{lemma}
\fi

@@

\begin{definition}
For each admissible $S\subset X_0$ and $T_1\subset X_0\setminus S$ with injective $r_{S,T_1}$ we also have the injectivity of $r_{S,T_2}$ for every $T_1 \subset T_2$. Therefore,  we can find a finite subset $T\subset X_0\setminus S$ such that both $r_{S,T}$ and $r_{S',T'}$ are injective. Such a $T$ will be called $S$-\textit{admissible} and $(S,T)$ is called \textit{admissible pair}.
\end{definition}
